Title

### 2015-12-09 paper/paper.tex
more on subgraph selections; going to talk about discrete optimization as well

For subgraph selection, we use a logistic regression model.

\subsection{Subgraph Ordering}

>>>>

For subgraph selection, we use a logistic regression model. We assumed that the
AMR subgraphs in each of the paragraphs was the correct partitioning of the
merged graph. This means that we had only positive examples in the training
set, so we added negative examples by creating up to $k=100$ other
partitionings of the same merged graph.

Features included the length of the pairwise subgraph similarity, and pairwise
verb overlap between the subgraphs. To determine subgraph similarity, we used
Jaccard similarity, defined to be:
$$J(A,B) = \frac{\lvert A \cap B \rvert}{\lvert A \cup B \rvert}$$

\subsection{Subgraph Ordering}
\subsection{Discrete Optimizations}
